\documentclass[11pt]{article}
\usepackage{cite}
\usepackage{comment}

\includecomment{comment}


\begin{document}

\title{The Sources}
\author{Pengyun Ji}
\maketitle

 The handbook chapter ``Fundaments of Branching Heuristics'' currently I am working on, except the paper version on my hand, I found that in different locations with different citations. one is ~\cite{kullmann2009fundaments}, and the other one is ~\cite{DBLP:series/faia/Kullmann09}.


\begin{comment}
The one ~\cite{kullmann2009fundaments} is found on google scholar, the one ~\cite{DBLP:series/faia/Kullmann09} is found on dblp.
Not know which citation can be officially used in paper.
\end{comment}


\section{The Handbook Chapter Citations}

\begin{comment}
Here I enter into the references in the handbook chapter.
But the formats of references are different due to using different searching engines.
Some links of the article can be open but some can not since it needs to buy. The question is same as beginning: which are offical in general paper/article?
\end{comment}

\begin{enumerate}
\item \cite{andrew1983handbook}
\item \cite{DBLP:conf/sat/BjesseKDSZ03}
\item \cite{beame2004towards}
\item \cite{DBLP:journals/rsa/BraunsteinMZ05}
\item \cite{bullen2013handbook} can only find 2013 version, publish by Springer Science \& Business Media, which is different with the one in handbook chapter. What we can do if can not find the original one in handbook chapter?
\item \cite{cull2005difference}
\item \cite{dubois1993sat}
\item \cite{DBLP:journals/talg/Eppstein06}
\item \cite{DBLP:conf/sat/EenS03}
\item \cite{DBLP:journals/eatcs/FominGK05}
\item \cite{DBLP:journals/jucs/FrancoKSWDV04}
\item The one in handbook chapter [Fre95] can not be found.
\item \cite{DBLP:conf/date/GoldbergN02} Sometimes search in dblp it has two parts in one citation [GN02], first part contains author with doi; second part contains publisher with ISBN.
\item \cite{gu1996algorithms} and \cite{du1997satisfiability}, a little confusing that these two are separated by one reference searching which in handbook chapter citation [GPFW97]
\end{enumerate}


\section{A list of missing proofs}

\begin{enumerate}
\item proof of lemma 7.3.1
\item proof of lemma 7.4.1
\item proof of corollary 7.4.2
\item proof of lemma 7.4.4 and 7.4.5
\item proof of lemma 7.4.7 in part.2
\item proof of lemma 7.4.9
\end{enumerate}





\bibliography{database}{}
\bibliographystyle{plain}
\end{document}
